Twitter Trader - Correlating \\ Stocks with Twitter Activity

### 2012-11-16 paper/paper.tex
added import to paper
updated references in paper

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\nocopyright
\frenchspacing
\pdfinfo{
/Title (Twitter Trader)
/Subject (AAAI Publications)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

@@

\subsection{Anticipated Results}
Based on prior research by Ruiz and Hristidis[1], we expect to find a small but exploitable correlation between the volume and positivity of tweets about a company, and its stock price one to three days in the future. This is based on a close examination Table 8 from Ruiz and Hristidis which shows not only a significant correlation of 0.12 between activity and stock price the same day for the DEG.-STD, but smaller correlations of 0.10 and 0.07 for one day and two days in the future respectively. At three days the correlation is -0.04 and is no longer significant.

@@

\textbf{2) Develop web interface for tracking sentiment and volume of tweets} \\
We plan to filter the Twitter live stream for all tweets about the following companies:

Amazon Boeing Cerner Coke Costco Dollar Tree eBay Ford Garmin Google HyVee Microsoft Monsanto Netflix Starbucks Travel Zoo Verizon Walmart Xerox

\"About\" here is as classified by our models. We will classify each tweet's sentiment and store the statistics for 6-hour intervals. We will provide an interface for viewing this sentiment data graphically over time, as compared to stock market prices and the volume of tweets about each company.

@@

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}

\nocopyright
\frenchspacing
\pdfinfo{
/Title (Twitter Trader)
/Subject (AAAI Publications)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

@@

\subsection{Anticipated Results}
Based on prior research by J. Bollen, H. Mao, and X.-J. Zeng[1], we expect to find a small but exploitable correlation between the volume and positivity of tweets about a company, and its stock price one to three days in the future. This is based on a close examination Table 8 from Ruiz and Hristidis which shows not only a significant correlation of 0.12 between activity and stock price the same day for the DEG.-STD, but smaller correlations of 0.10 and 0.07 for one day and two days in the future respectively. At three days the correlation is -0.04 and is no longer significant.

@@

\textbf{2) Develop web interface for tracking sentiment and volume of tweets} \\
We plan to filter the Twitter live stream for all tweets about the following companies: \\

Amazon Boeing Cerner Coke Costco Dollar Tree eBay Ford Garmin Google HyVee Microsoft Monsanto Netflix Starbucks Travel Zoo Verizon Walmart Xerox \\

"About" here is as classified by our models. We will classify each tweet's sentiment and store the statistics for 6-hour intervals. We will provide an interface for viewing this sentiment data graphically over time, as compared to stock market prices and the volume of tweets about each company.

@@

[1] J. Bollen, H. Mao, and X.-J. Zeng. Twitter mood predicts the
stock market. Journal of Computational Science,
abs/1010.3003, 2010\\

[2] Mallett, University of Massachussetts Department of Computer Science\\

[3] Sanders Analytics (http://www.sananalytics.com/lab/twitter-sentiment/)
